---
title: "a3_task3_mukta_kelkar"
author: "Mukta Kelkar"
date: "10/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(kableExtra)
library(lubridate)
library(data.table)
```

### Preliminary Steps

Read in the urchins data and change the headers to lowercase_snake_case

```{r}
urchins <- read.csv(here("data", "urchins.csv")) %>% 
  clean_names()
```

### Section 1

Here I do exploratory data visualizations using *geom_histogram* and *geom_boxplot*

```{r}
urchins %>% 
  ggplot(aes(x = size))+
  geom_histogram() +
  facet_wrap (~common_name)

urchins %>% 
  ggplot(aes(x = common_name, y = size)) +
  geom_boxplot()
```

Next, I make a table of descriptive statistics

```{r}
urchins_stats <- urchins %>% 
  group_by(common_name) %>% 
  summarize(
    mean_size = mean(size),
    median_size = median(size),
    sd_size = sd(size),
    sample_size = n()
  )

kbl(urchins_stats)
```

Overall, it looks like the mean size of the red urchin is larger than that of the purple urchin. The population of red urchin has a wider spread than that of the purple urchin The actual difference in mean urchin diameter is 2.3, the % difference is _____.


### Section 2:

Explore purple urchin counts by site and year

```{r}
purple_urchins <- urchins %>% 
  filter(common_name == "Purple Urchin") %>% 
  mutate(mdy(date)) %>%
  rename(date_format = "mdy(date)") %>% 
  mutate(year = year(date_format)) %>% 
  mutate(site_full = case_when(
    site == "NAPL" ~ "Naples Reef",
    site == "AQUE" ~ "Arroyo Quemado Reef",
    site == "CARP" ~ "Carpinteria Reef",
    site == "MOHK" ~ "Mohawk Reef",
    site == "IVEE" ~ "Isla Vista Reef"
    ))
```

#COME BACK TO THIS SECTION AND MAKE IT NOT A HEADER
-need to figure out how to change a data frame into a summary table

```{r}
purple_urchin_stats <- purple_urchins %>% 
    count(site_full, year) %>% 
    group_by(site_full)

purple_summary <- as.data.table(purple_urchin_stats)
```

Make an exploratory graph

```{r}
purple_summary %>% 
  ggplot(aes(x = year, y = n)) +
  geom_jitter(aes(color = site_full), size = 3) +
  labs(x = "Year",
       y = "Number of Urchins")
```




